### 2022-11-26 ms.rmd
Added node labels = NULL and added a models with scaled variables to make it easier to check correlation at phlo level

# Ultrametric?
is.ultrametric(tree) # nope

# Grab phylo matrix
phy_vcv <- vcv(tree)

>>>>

# Ultrametric?
is.ultrametric(tree) # nope
tree2 <- force.ultrametric(tree, method = "extend")

# Grab out data
   data <- read.csv("./data/drosi_data.csv")

# functions
source("./R/func.R")
t <- tree_checks(tree2, data = data, dataCol = "species", type = "check")
data <- data %>% mutate(species = gsub(" ", "", species),
                        phylo = species,
                        obs = 1:n()) %>% filter(!species %in% t$Species_InData_But_NotTree) 
tree3 <- tree_checks(tree2, data = data, dataCol = "species", type = "prune")
tree_checks(tree3, data = data, dataCol = "species", type = "check")
# Grab phylo matrix
phy_vcv <- vcv(tree3, cor = FALSE)
tree3$node.label <- NULL

```{r}

#### Try MCMCglmm which I expect will be MUCH faster. Deals with missing data using data augmentation
rerun = FALSE
if(rerun){
  prior = list(R = list(V = diag(3), nu=1.002), 
             G = list(G1=list(V = diag(3), nu = 1.002)))

data$animal = data$phylo

mcmcglmm_model <- MCMCglmm::MCMCglmm(cbind(ctmax, cfts, tdt_z) ~ -1 + trait, random = ~us(trait):animal, rcov = ~us(trait):units ,pedigree=tree3,burnin=1000, nitt = 300000, thin = 5, family = rep("gaussian", 3), prior = prior, pl = TRUE, pr = TRUE, data = data)

# We'll also z-transofmr to make the coprrelation stuff easier to calculate. 
data <- data %>% mutate(z_ctmax = scale(ctmax),
                         z_cfts = scale(cfts),
                        z_tdt_z = scale(tdt_z))

mcmcglmm_model_z_trans <- MCMCglmm::MCMCglmm(cbind(z_ctmax, z_cfts, z_tdt_z) ~ -1 + trait, random = ~us(trait):animal, rcov = ~us(trait):units, pedigree=tree3,burnin=1000, nitt = 300000, thin = 5, family = rep("gaussian", 3), prior = prior, pl = TRUE, pr = TRUE, data = data)

saveRDS(mcmcglmm_model, file = "./output/model/mcmcglmm_model")
saveRDS(mcmcglmm_model_z_trans, file = "./output/model/mcmcglmm_model_z_trans")
} else{
  mcmcglmm_model <- readRDS("./output/model/mcmcglmm_model")
}

# Extract estimates
sol <- mcmcglmm_model$Sol
vcv <- mcmcglmm_model$VCV

# Extract the estmated / imputaed Z for each species, but drop internal ancestral nodes
z <- sol[, grep("traittdt_z.animal", colnames(sol))]
z <- z[,-grep("Node", colnames(z))]
head(z)

# Clean up names so they are just species names
